### 2023-04-16 paper/language.tex
explanation of with-in construct and how it relates to layout values and function calls in PikaCore

>>>>

There is only one situation in \PikaCore{} in which layouts can be applied. This is when a function
is called. A function, generally, takes at least one layout value as input and produces a layout value as
output. The \verb|with-in| construct allows both of the input and output layouts to be applied with
appropriate variables, representing the input and output variables that the function will use when
it's called.

For example, given a function

\begin{align*}
  &f\; \{ x \mapsto a \} := \sslmath{y, z}{(y+1) \mapsto a, z \mapsto w}
\end{align*}

\noindent
we can apply it like this

\begin{align*}
  \withIn{\{p, q\} := f\; \{s\}} e
\end{align*}

\noindent
If $s$ is nonzero (meaning $s$ points to something and this branch of $f$ is actually used), this will result in an SSL assertion
for the input $\{s \mapsto a\}$ and an SSL assertion for the output $\{p \mapsto a, q \mapsto w\}$ where $w$ is fresh. These
SSL assertions are combined with the SSL assertion given by the expression $e$.
